---
title: "Diversity"
author: "Jonathan Bourne"
date: "25 May 2016"
output: html_document
---


deprivation link
https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/467767/File_4_ID_2015_Sub-domains_of_deprivation.xlsx


2001 census data
http://neighbourhood.statistics.gov.uk/dissemination/DownloadData.zip?$ph=60_61_64_65&step=6&downloadLargeFile=true&fileIndex=1

Converting 2001 LSOA to 2011 LAD's
http://webarchive.nationalarchives.gov.uk/20160105160709/http://www.ons.gov.uk/ons/external-links/other/2001-lower-layer-super-output-areas--lsoa--to-2011-lsoas-and-lads.html


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Setup}
packages <- c("dplyr", "magrittr", "tidyr", "ggplot2", "caret", "openxlsx", "maptools", "rgeos", "ggmap", "scales", "RColorBrewer", "xtable", "stargazer", "readr")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


lapply(packages, library, character.only = TRUE)

#Set up file system to read the correct folders this switches between aws and windows mode
if((Sys.info()[1]=="Linux")){
basewd <-"~/Dropbox/DiversityAWS"} else{
 basewd <- "C:/Users/pc1/Dropbox/DiversityAWS"
}
DataFolder <- file.path(basewd, "Data")
ShapeFiles <- file.path(DataFolder,"ShapeFiles")
Figures <- file.path(basewd, "Figures")
Data2001 <- file.path(DataFolder, "Census2001")
select <-dplyr::select

```


```{r}
setwd(DataFolder)

deprivation <-read.xlsx("File_4_ID_2015_Sub-domains_of_deprivation.xlsx", sheet = 2)
  deprivationLAD<-read.xlsx("File_10_ID2015_Local_Authority_District_Summaries.xlsx", sheet = 2)
```

Get Census Data This doesn't work
```{r}

temp <- tempfile()
download.file("http://neighbourhood.statistics.gov.uk/dissemination/DownloadData.zip",temp, mode = "wb")
con <- unz(temp, "UV090301_88_GeoPolicy_UK_LSOA.CSV")
unzip(temp, "UV090301_88_GeoPolicy_UK_LSOA.CSV")
dd <- read.table("UV090301_88_GeoPolicy_UK_LSOA.CSV", 
                 sep = ",", 
                 skip = 5, 
                 header = T)
unlink(temp)

```

#Ratio of median house price to median earnings


```{r}
dt <- "https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/85872/table577.xls"
dat <- read(dt)
dat <- read.xls (dt, sheet = 1, header = TRUE)
```


Open 2001 ethnicity tables
```{r}
setwd(DataFolder)
download.file("http://neighbourhood.statistics.gov.uk/dissemination/DownloadData.zip", "test")

setwd(Data2001)
#unzip folder
con <- unz(description="DownloadData.zip", filename="UV090301_88_GeoPolicy_UK_LSOA.txt")
unzip("DownloadData.zip")

#import and fix headers
Census2001 <-read.csv("UV090301_88_GeoPolicy_UK_LSOA.CSV", skip = 5)
names(Census2001)[13:ncol(Census2001)] <-make.names(read_csv("UV090301_88_GeoPolicy_UK_LSOA.CSV", skip =1,n_max =1))[13:ncol(Census2001)]



```

NOt Ueful in Main analaysis
```{r}

setwd(DataFolder)

basedata <- read.xlsx("ward-atlas-data.xlsx", startRow = 3, cols=1:36, sheet = 2)

#Extract from the ward level data information on Area and ethnicity, create a white british variable that is distinct from White. Calculate the gini coefficients
ward <- basedata  %>%
  select(Codes:Square.Kilometres, White:Other.White) %>% select(-c(White.British:White.Gypsy.or.Irish.Traveller)) %>% 
  mutate(White.British = White-Other.White) %>%
  mutate(Total =  rowSums(.[8:13]), ginisimpethnic = 1-rowSums((.[7:11])^2)/Total^2,ginisimp= 1-rowSums((.[8:13])^2)/Total^2)


London <- ward %>% filter(is.na(Borough))

ward %<>% filter(!is.na(Borough))

#Create a Dataset that is for london Bouroughs
borough <- ward %>% select(-Names) %>% group_by(Borough) %>% 
  mutate(fract = Total/sum(Total), ginisimpethnic=ginisimpethnic*fract, ginisimp =ginisimp*fract) %>%
summarise_each(funs(sum),Hectares:ginisimp ) %>% 
  mutate(borginisimpethnic = 1-rowSums((.[4:8])^2)/Total^2,
         borginisimp= 1-rowSums((.[5:10])^2)/Total^2,
         ratioethnic = ginisimpethnic/borginisimpethnic,
         ratio = ginisimp/borginisimp) 

#Construct a single entity that gives the index for the whole of london
London <- borough %>% mutate(fract = Total/sum(Total), ginisimpethnic=ginisimpethnic*fract,
                             ginisimp =ginisimp*fract, 
                             borginisimpethnic=borginisimpethnic*fract, 
                             borginisimp =borginisimp*fract) %>% 
  summarise_each(funs(sum),Hectares:borginisimp ) %>% 
  mutate(cityginisimpethnic = 1-rowSums((.[3:7])^2)/Total^2,
         cityginisimp= 1-rowSums((.[4:9])^2)/Total^2,
         ratioethnic = ginisimpethnic/cityginisimpethnic,
         ratio = ginisimp/cityginisimp)

```

#Maximum Diversity 
As diversity is relative to perfectly equal weights diversity is maximised at the total maximum number of ethnicities. in this model there are two different numbers one for seperating White British from White (Brexit model) and the other where all described as white are included in a single group (Visible ethnic minorirty model.)
```{r}
#in the White British and not White model
#LADginisimp
1-2*(1/2)^2

#white british and white model
#LADginisimpethnic
1-6*(1/6)^2

```

#England and wales integration


```{r}
#length(readLines("KS201EWDATA.CSV")) #total number of lines in the file
```

Import England and wales
```{r}
#Output area data
Kdata <- read.csv("KS201EWDATA.CSV", stringsAsFactors = FALSE) 

#Column names
Kdesc <- read.csv("KS201EWDESC0.CSV", stringsAsFactors = FALSE) 

#Built up area association
BUA <- read.csv("OA11_BUASD11_BUA11_LAD11_RGN11_EW_LU.csv", stringsAsFactors = FALSE)
```


```{r}
#Subset the data frame to take only the columns involving the ethnicities we are interested in
Kpercs <- Kdata[,c(1:2,21:38)]
names(Kpercs)[-1] <- make.names(Kdesc[c(1,20:37), 4])

#The ethnicities are two detailed we will combine the subgroups into larger ethnic groups
Kpercs %<>% transmute(GeographyCode = GeographyCode,
                      TotalPop = All.categories..Ethnic.group,
                          Asian = rowSums(select(.,starts_with("Asian"))),
                          Black = rowSums(select(.,starts_with("Black"))),
                          Mixed = rowSums(select(.,starts_with("Mixed"))),
                          Other= rowSums(select(.,starts_with("Other"))),
                          White = rowSums(select(.,starts_with("White"))),
                          WhiteBrit = White,
                          White.Other = White..Other.White,
                          WhiteBrit= WhiteBrit-White.Other) %>%
  mutate_each(funs(./100), -GeographyCode, -TotalPop)

#Calculate the Gini coefficient
Kpercs %<>% mutate(ginisimpethnic= 1-rowSums(.[,c(3:6,8:9)]^2),
                   ginisimp=1-((1-WhiteBrit)^2 + WhiteBrit^2) )
names(Kpercs)[1] <- "OA11CD" #there is some bug which means the header needs to be renamed before merging
Kpercs %<>% inner_join(., BUA, by = "OA11CD")


#LAD stands for local aurthority district. This peice of code allows for the whole of london to be treated as a single unit by mergeing there codes into a single "London"
LADS <- BUA %>% mutate(islondon= ifelse(RGN11CD =="E12000007","E12000007" ,LAD11CD),
                       islondonNM= ifelse(RGN11CD =="E12000007","London" ,LAD11NM)
                       )%>% 
  group_by(LAD11CD) %>% 
  summarise_each(funs(first), LAD11NM,RGN11CD, RGN11NM, islondon, islondonNM)

#LAD diversity
LADdiv <- Kpercs %>% group_by(LAD11CD) %>% mutate(fract = TotalPop/sum(TotalPop)) %>%
                    mutate_each( funs(.*fract), Asian:ginisimp)  %>% summarise_each(funs(sum),TotalPop:ginisimp ) %>% 
  mutate(LADginisimpethnic= 1-rowSums(.[,c(3:6,8:9)]^2),
                   LADginisimp=1-((1-WhiteBrit)^2 + WhiteBrit^2) ,
         ratioethnic = ginisimpethnic/LADginisimpethnic,
         ratio = ginisimp/LADginisimp)

```


London as a single unit
```{r}
#London chunked as 1 block
LADSLON <- LADS %>% group_by(islondon) %>% 
  summarise_each(funs(first), RGN11CD, RGN11NM, islondonNM)

LADdivlon <- Kpercs %>% mutate(islondon= ifelse(RGN11CD =="E12000007","E12000007" ,LAD11CD))%>%
  group_by(islondon) %>% mutate(fract = TotalPop/sum(TotalPop)) %>%
                    mutate_each( funs(.*fract), Asian:ginisimp)  %>% summarise_each(funs(sum),TotalPop:ginisimp ) %>% 
  mutate(LADginisimpethnic= 1-rowSums(.[,c(3:6,8:9)]^2),
                   LADginisimp=1-((1-WhiteBrit)^2 + WhiteBrit^2) ,
         ratioethnic = ginisimpethnic/LADginisimpethnic,
         ratio = ginisimp/LADginisimp) %>% inner_join(.,LADSLON, by="islondon")

```


glm for fit
```{r}
predmod <-train(x =select(LADdivlon, ginisimp, LADginisimp), y = LADdivlon$ratio, method = "glm" )

gini2 <- (LADdivlon$LADginisimp)^2
predmod3 <- lm( LADdivlon$ginisimp ~  LADdivlon$LADginisimp+ gini2 +0)


gini3 <- (LADdiv$LADginisimp)^2
predmod4 <- lm( LADdiv$ginisimp ~  LADdiv$LADginisimp+ gini3 +0)


    LADdivlon<-   LADdivlon %>% bind_cols(.,  data.frame(
  predictedratio = predict(predmod, select(.,ginisimp, LADginisimp)),
  predictedgini= predict(predmod3, select(.,ratio, LADginisimp)))) %>% 
      mutate(pred.gin.rat =ifelse(predictedgini/LADginisimp>1, 1, predictedgini/LADginisimp), seg.int.rat = (ratio-pred.gin.rat)/pred.gin.rat )%>% mutate(islondonNM = sub(", City of", "", islondonNM), islondonNM = sub(" with Darwen", "", islondonNM))
    

    LADdiv<-   LADdiv %>% bind_cols(.,  data.frame(
  predictedgini= predict(predmod4, select(.,ratio, LADginisimp)))) %>% 
      mutate(pred.gin.rat =ifelse(predictedgini/LADginisimp>1, 1, predictedgini/LADginisimp), seg.int.rat = (ratio-pred.gin.rat)/pred.gin.rat )%>% 
      inner_join(.,LADS, by="LAD11CD") %>%
      mutate(LAD11NM = sub(", City of", "", LAD11NM), LAD11NM = sub(" with Darwen", "", LAD11NM))

    
    
```

Biggest cities
```{r}
#"Sheffield","Leicester",
Cities <- c("London", "Birmingham", "Leeds",  "Bradford", "Manchester", "Liverpool", "Bristol","Cardiff",  "Oldham", "Blackburn", "Burnley", "Oxford")


```

#Figure of diversities
The below figure plots all the largest cities in England and Wales against a general linear model of uk diversity, and the line of perfect integration.
```{r Diversity Model}

ggplot(LADdivlon, aes(x=LADginisimp, y=ginisimp)) +geom_point(alpha = 0.2) + ggtitle("English/Welsh Ethnic \nDiversity, across Cities and Counties")+ ylab("Neighbourhood") +xlab("Borough/County") + 
  geom_abline(intercept= 0, slope = 1, linetype =2) +
  geom_line(aes(x= LADginisimp, y= predictedgini), color = "red")+ 
  geom_point(data = filter(LADdivlon,islondonNM %in% Cities), aes(x=LADginisimp, y=ginisimp))+
  geom_text(data = filter(LADdivlon,islondonNM %in% Cities), 
            aes(x=LADginisimp, y=ginisimp, label=islondonNM ),
            vjust = 0, nudge_y = -0.03)
setwd(Figures)
ggsave("SegIndex.png")
```

#create a coloured map of British diversity

The instructions for doing this come from 
http://www.r-bloggers.com/mapping-with-ggplot-create-a-nice-choropleth-map-in-r/

```{r}

setwd(ShapeFiles)
states.shp <- readShapeSpatial("Local_UnitaryAuthority.shp")
names(states.shp)
print(states.shp$NAME)
print(states.shp$CODE)

mapdata<- data.frame(CODE = as.character(states.shp$CODE) ) %>% 
  left_join(., select(LADdiv, LAD11CD, ratio), by =c("CODE" ="LAD11CD")) 

#delete?
mapdata<- data.frame(CODE = as.character(states.shp$CODE) ) %>% 
  left_join(., LADdiv, by =c("CODE" ="LAD11CD")) 


states.shp.f <- fortify(states.shp, region = "CODE")

merge.shp.coef <- right_join(states.shp.f, mapdata, by = c("id"="CODE"))

final.plot <- merge.shp.coef[order(merge.shp.coef$order), ] 
sewd(DataFolder)
saveRDS(final.plot, file = "britaindataframe.rds" )
#final.plot <- readRDS("britaindataframe.rds")

setwd(Figures)
ggplot(data = final.plot[!is.na(final.plot$ratio),], 
       aes(x = long, y = lat, group = group)) + geom_path() +
  geom_polygon(aes(fill = seg.int.rat)) + scale_fill_gradient2(low = "red", high = "blue")+
    ggtitle("Map of England and Wales Local authorities \nby Integration Index")
ggsave("Integration.png")

ggplot(data = final.plot[!is.na(final.plot$ratio),], aes(x = long, y = lat, group = group)) + geom_path() +
  geom_polygon(aes(fill = LADginisimp)) + scale_fill_gradient2(low = "green", high = "blue")+ 
  ggtitle("Map of England and Wales Local authorities \nby diversity score ")
ggsave("Diversity.png")


ggplot(data = filter(final.plot, RGN11CD == "E12000007"), aes(x = long, y = lat, group = group)) + geom_path() +
  geom_polygon(aes(fill = seg.int.rat)) + scale_fill_gradient2(low = "red", high = "blue") + 
  ggtitle("Map of London's Local authorities \nby diversity score ")
ggsave("DiversityLondon.png")

#test2 <-filter(test, RGN11CD == "E12000007")

```



where are white Brits a minority
```{r}

Wmin <- Kpercs %>% filter(WhiteBrit<0.5)

#Average percent of each lsoa
mean(Kpercs$WhiteBrit)

#The fraction of LSOA's that white british make up less than 50% of the population
nrow(Wmin)/nrow(Kpercs)

#White Britons make up the following percentage of areas where they are less than 50%
sum(Wmin$TotalPop*Wmin$WhiteBrit)/sum(Wmin$TotalPop)

# 
sum(Wmin$TotalPop)/sum(Kpercs$TotalPop)

#Percent of white britons living in an area where they are a minority
sum(Wmin$TotalPop*Wmin$WhiteBrit)/sum(Kpercs$TotalPop*Kpercs$WhiteBrit)
#Percent of everyone else living in an area where they are a minority
1-sum(Wmin$TotalPop*(1-Wmin$WhiteBrit))/sum(Kpercs$TotalPop*(1-Kpercs$WhiteBrit))

ggplot(Kpercs, aes(x=WhiteBrit*100), fill = blue) +
  geom_density(fill = "steelblue", alpha = 0.5) +
  labs(title = "White British as a percentage\n of the local population", x = "White British as percentage of Population") +
  geom_segment(aes(x = mean(Kpercs$WhiteBrit)*100, y = 0, xend = mean(Kpercs$WhiteBrit)*100, yend = 0.05, colour = "segment")) + 
  theme(legend.position ="none") +
  annotate("text", x = mean(Kpercs$WhiteBrit)*100, y = 0.06, label = paste("Average",round(mean(Kpercs$WhiteBrit)*100), "%"))
ggsave("WhiteBritArea.png")

ggplot(Wmin, aes(x=WhiteBrit*100), fill = blue) +
    geom_density(fill = "steelblue", alpha = 0.5) +
  ggtitle("White British as a percentage\n of the local population where White British\n is less than 50% of the local population")

#White British make up less than x in y LSOA

WhiteBritPerc <- data.frame(LessThan = seq(0,1, 0.05)*100,  Percentage =  sapply(seq(0,1, 0.05), function(n){
  sum(Kpercs$WhiteBrit > n)/nrow(Kpercs)
}) %>% round(.,3) * 100
)

WhiteBritPerc %>% ggplot(., aes(x = LessThan, y = Percentage)) + geom_line() +
  labs(title = "White British ", y = "Percentage of LSOA's",
       x = "White British as % of population")

```

Brexit Votes
```{r}

BrexitVotes <-read.csv("http://www.electoralcommission.org.uk/__data/assets/file/0014/212135/EU-referendum-result-data.csv")

BrexitVotes <-BrexitVotes %>% rename(LAD11CD = Area_Code) %>% 
  select(LAD11CD, Pct_Remain) %>% 
  left_join(LADdiv ,., by = "LAD11CD") %>% filter(!is.na(Pct_Remain))

set.seed(1223)
 trainsamp<-createDataPartition(BrexitVotes$Pct_Remain, p = 0.5, list =F)

Mod1 <- train(x=select(BrexitVotes, ginisimp,  seg.int.rat)[trainsamp,],
              y=BrexitVotes$Pct_Remain[trainsamp],
       method ="lmStepAIC")

preds1 <- predict(Mod1, BrexitVotes[-trainsamp,])

postResample(preds1, BrexitVotes$Pct_Remain[-trainsamp])
summary(Mod1)

coef(Mod1$finalModel)
```

```{r}
BrexitVotes2 <- BrexitVotes %>% mutate(Pct_Remain = as.factor(Pct_Remain>50))

set.seed(1223)
trainsamp<-createDataPartition(BrexitVotes2$Pct_Remain, p = 0.6, list =F)


Mod2 <- train(x=select(BrexitVotes2, LADginisimp, seg.int.rat)[trainsamp,] %>% as.data.frame,
              y=(BrexitVotes2$Pct_Remain[trainsamp]),
       method ="glm", family="binomial")

preds2 <- predict(Mod2, BrexitVotes2[-trainsamp,])

confusionMatrix(preds2, BrexitVotes2$Pct_Remain[-trainsamp]) 

confusionMatrix(preds2, BrexitVotes2$Pct_Remain[-trainsamp])$table %>% 
  as.data.frame %>% spread(key = Reference, value = Freq)%>% stargazer(type = "html", summary = FALSE, rownames = FALSE)


summary(Mod2)
coef(Mod2$finalModel)
```


Include deprivation index.
```{r}
names(deprivationLAD)[c(1,4)] <-c("LAD11CD", "RankDepriv")

names(deprivationLAD) <- make.names(names(deprivationLAD))

deprivationLAD <- deprivationLAD  %>%
  left_join(., BrexitVotes2, by ="LAD11CD")

set.seed(1223)
trainsampDep<-createDataPartition(deprivationLAD$Pct_Remain, 
                                  p = 0.6, list =F)


ModDepriv <-deprivationLAD %>% 
  select( LADginisimp, seg.int.rat, RankDepriv) %>% 
  slice(trainsampDep) %>% train(x=. ,
              y=(deprivationLAD$Pct_Remain[trainsampDep]),
       method ="glm", family="binomial")

predsDepriv <- predict(ModDepriv, deprivationLAD[-trainsampDep,])

confusionMatrix(predsDepriv, deprivationLAD$Pct_Remain[-trainsampDep]) 

summary(ModDepriv)

#Essentially higher levels of ethniv diveristy at LAD level and higher levels of segregation increase the probabilioty of voting out. deprivation is significant but has a weak effect increasing likelyhood of voting out as deprivation DECREASES, this is likely to be due to some interaction effect.

#All deprivation indices are highly corrallated 
cormat <-cor(deprivationLAD[3:12])

```



Table of the most and least integrated
```{r}
test <- BrexitVotes %>% arrange(seg.int.rat) %>% 
  select(RGN11NM, LAD11NM, seg.int.rat, Pct_Remain) %>%
  setNames(c("Region", "County/Borough", "Index", "Brexit")) %>%
  mutate(Index = round(Index, 2), Brexit = if_else(Brexit>50, "In", "Out")) %>%
  slice(1:10) %>% stargazer(type = "html", summary = FALSE)
  
MostInt <- BrexitVotes %>% arrange(desc(seg.int.rat)) %>% 
  select(RGN11NM, LAD11NM, seg.int.rat, Pct_Remain) %>%
  setNames(c("Region", "County/Borough", "Index", "Brexit")) %>%
  mutate(Index = round(Index, 2), Brexit = if_else(Brexit>50, "In", "Out"))

MostInt %>%  slice(1:10) %>% stargazer(type = "html", summary = FALSE)

setwd(Figures)
MostInt %>% ggplot(., aes(x= Brexit, y= Index, fill = Brexit)) + geom_boxplot() + 
  labs(title ="Brexit vote by Integration score", 
       x = "Brexit Vote", 
       y= "Integration Index Score") + 
  theme(legend.position ="none")
ggsave("BrexitIntScore.png")

t.test(MostInt$Index[MostInt$Brexit == "In"],
       MostInt$Index[MostInt$Brexit == "In"],
       alternative = "greater")


```


